GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D

### 2025-01-06 main.tex
correct tbl ref

To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape. 
The characteristics of them are shown in Table~\ref{tlb:1} and the examples are shown in Figure~\ref{fig:raw86}.

% table 1
\begin{table}[h]
    \centering
    \caption{Comparison of the characteristics of the four species of fresh grape}
    \begin{tabular}{cccc}
        \hline
        \textbf{Grape Species} & \textbf{Color} & \textbf{Sparsity} & \textbf{Shape} \\
        \hline
        Red & Purple-red & Sparser & Ellipsoid \\
        Green & Green & Sparse & Ellipsoid \\
        Kyoho & Dark-purple & Dense & Sphere \\
        Shine-Muscat & Green & Very dense & Sphere \\
        \hline
    \label{tlb:1}
    \end{tabular}
\end{table}

@@

For whole bunch multi-view images acquisition, the device was built as shown in Figure~\ref{fig:raw9}a. 
One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig.~\ref{fig:raw9}a1) that can achieve rotation at a certain speed. 
The entire device was placed in front of a solid-colored backdrop (Fig.~\ref{fig:raw9}a2), and multiple cameras were set up to photograph the bunch from different height angles. 
In addition, a ruler with markers were used for scale correction. 
For single complete berry multi-view images acquisition in batch (Fig.~\ref{fig:raw9}b). 
Nine berries were fixed floating by needle disk (Fig.~\ref{fig:raw9}b1) on a turntable device (Fig.~\ref{fig:raw9}b2). 
The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tlb:2}. 
Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure~\ref{fig:raw10}.

% table 2
\begin{table}[h]
    \centering
    \caption{Comparison of the characteristics of the four species of fresh grape}
    \begin{tabular}{cccc}
        \hline
        \textbf{Object} & \textbf{Shooting distance} & \textbf{Shooting angle} & \textbf{Number of images} \\
        \hline
        Bunch        & 25-60cm & $0^{\circ}$, $\pm 25^{\circ}$, $\pm 45^{\circ}$ & $5 \times 50$ \\
        Single berry & 20-40cm & $-15^{\circ}$, $0^{\circ}$, $25^{\circ}$, $45^{\circ}$ & $4 \times 50$ \\
        \hline
    \label{tlb:2}
    \end{tabular}
\end{table}

@@

Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in 
%todo
Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tlb:3}.

% table 3
\begin{table}[h]
    \centering
    \caption{Instance berry segmentation results from whole bunch}
    \begin{tabular}{ccc}
        \hline
        \textbf{Model} & \textbf{Class} & \textbf{AP@50:5:95} \\
        \hline
        \multirow{2}{*}{SoftGroup \citep{vu_softgroup_2022}} & Berry & 0.995 \\
        \cline{2-3}
        & Stem & 0.941 \\
        \hline
    \end{tabular}
\end{table}

As can be seen from Table~\ref{tlb:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch. The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure~\ref{fig:raw13}.

@@

Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tlb:4}. 
GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure~\ref{fig:raw14}.

% table 4
\begin{table}[h]
    \centering
    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud}
    \begin{tabular}{cccccc}
        \hline
        \textbf{Model} & \textbf{DataSet} & \textbf{CD-distance $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
        \hline
        \multirow{2}{*}{PoinTr} & Test & 9.036 & 0.721 & 0.705 & 0.713 \\
        \cline{2-6}
        & Inference & 10.542 & 0.623 & 0.601 & 0.612 \\
        \hline
        \multirow{2}{*}{SnowFlakeNet} & Test & 11.235 & 0.512 & 0.534 & 0.521 \\
        \cline{2-6}
        & Inference & 12.384 & 0.415 & 0.423 & 0.419 \\
        \hline
        \multirow{2}{*}{TopNet} & Test & 23.019 & 0.201 & 0.200 & 0.201 \\
        \cline{2-6}
        & Inference & 31.88 & 0.155 & 0.154 & 0.154 \\
        \hline
        \multirow{2}{*}{GRNet} & Test & 19.24 & 0.402 & 0.392 & 0.397 \\
        \cline{2-6}
        & Inference & 21.25 & 0.365 & 0.363 & 0.364 \\
        \hline
        \multirow{2}{*}{GrapeCPNet (\textbf{Ours})} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
        \cline{2-6}
        & Inference & \textbf{9.158} & \textbf{0.685} & \textbf{0.696} & \textbf{0.689} \\
        \hline
    \end{tabular}
\end{table}

>>>>

To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape. 
The characteristics of them are shown in Table~\ref{tbl:1} and the examples are shown in Figure~\ref{fig:raw86}.

% table 1
\begin{table}[h]
    \centering
    \caption{Comparison of the characteristics of the four species of fresh grape}
    \begin{tabular}{cccc}
        \hline
        \textbf{Grape Species} & \textbf{Color} & \textbf{Sparsity} & \textbf{Shape} \\
        \hline
        Red & Purple-red & Sparser & Ellipsoid \\
        Green & Green & Sparse & Ellipsoid \\
        Kyoho & Dark-purple & Dense & Sphere \\
        Shine-Muscat & Green & Very dense & Sphere \\
        \hline
    \label{tbl:1}
    \end{tabular}
\end{table}

@@

For whole bunch multi-view images acquisition, the device was built as shown in Figure~\ref{fig:raw9}a. 
One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig.~\ref{fig:raw9}a1) that can achieve rotation at a certain speed. 
The entire device was placed in front of a solid-colored backdrop (Fig.~\ref{fig:raw9}a2), and multiple cameras were set up to photograph the bunch from different height angles. 
In addition, a ruler with markers were used for scale correction. 
For single complete berry multi-view images acquisition in batch (Fig.~\ref{fig:raw9}b). 
Nine berries were fixed floating by needle disk (Fig.~\ref{fig:raw9}b1) on a turntable device (Fig.~\ref{fig:raw9}b2). 
The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tbl:2}. 
Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure~\ref{fig:raw10}.

% table 2
\begin{table}[h]
    \centering
    \caption{Comparison of the characteristics of the four species of fresh grape}
    \begin{tabular}{cccc}
        \hline
        \textbf{Object} & \textbf{Shooting distance} & \textbf{Shooting angle} & \textbf{Number of images} \\
        \hline
        Bunch        & 25-60cm & $0^{\circ}$, $\pm 25^{\circ}$, $\pm 45^{\circ}$ & $5 \times 50$ \\
        Single berry & 20-40cm & $-15^{\circ}$, $0^{\circ}$, $25^{\circ}$, $45^{\circ}$ & $4 \times 50$ \\
        \hline
    \label{tbl:2}
    \end{tabular}
\end{table}

@@

Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in 
%todo
Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tbl:3}.

% table 3
\begin{table}[h]
    \centering
    \caption{Instance berry segmentation results from whole bunch}
    \begin{tabular}{ccc}
        \hline
        \textbf{Model} & \textbf{Class} & \textbf{AP@50:5:95} \\
        \hline
        \multirow{2}{*}{SoftGroup \citep{vu_softgroup_2022}} & Berry & 0.995 \\
        \cline{2-3}
        & Stem & 0.941 \\
        \hline
    \end{tabular}
    \label{tbl:3}
\end{table}

As can be seen from Table~\ref{tbl:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch. The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure~\ref{fig:raw13}.

@@

Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tbl:4}. 
GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure~\ref{fig:raw14}.

% table 4
\begin{table}[h]
    \centering
    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud}
    \begin{tabular}{cccccc}
        \hline
        \textbf{Model} & \textbf{DataSet} & \textbf{CD-distance $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
        \hline
        \multirow{2}{*}{PoinTr} & Test & 9.036 & 0.721 & 0.705 & 0.713 \\
        \cline{2-6}
        & Inference & 10.542 & 0.623 & 0.601 & 0.612 \\
        \hline
        \multirow{2}{*}{SnowFlakeNet} & Test & 11.235 & 0.512 & 0.534 & 0.521 \\
        \cline{2-6}
        & Inference & 12.384 & 0.415 & 0.423 & 0.419 \\
        \hline
        \multirow{2}{*}{TopNet} & Test & 23.019 & 0.201 & 0.200 & 0.201 \\
        \cline{2-6}
        & Inference & 31.88 & 0.155 & 0.154 & 0.154 \\
        \hline
        \multirow{2}{*}{GRNet} & Test & 19.24 & 0.402 & 0.392 & 0.397 \\
        \cline{2-6}
        & Inference & 21.25 & 0.365 & 0.363 & 0.364 \\
        \hline
        \multirow{2}{*}{GrapeCPNet (\textbf{Ours})} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
        \cline{2-6}
        & Inference & \textbf{9.158} & \textbf{0.685} & \textbf{0.696} & \textbf{0.689} \\
        \hline
    \end{tabular}
    \label{tbl:4}
\end{table}
